---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

<<<<<<< HEAD
<<<<<<< HEAD
<<<<<<< HEAD
=======
>>>>>>> 4aec923a397186abcfb3323cfbff9642c7a0d504
```{r,}
library(classdata)
df = ames
str(ames)
```
1. We have the following variables - 
Parcel ID - Character    (House ID)
Address - Character      (Address of hosue in ames)
Style - Factor           (Dimensions and stuff)
Occupancy - factor       (Occupies or free)
Sale Date - Date         (Date of sale)
Sale Price - Numeric     (Price sold at)
Multi Sale - charater    (if sold multiple times)
YearBuilt - Numeric      (Year built in)
Acres - Numeric          (Area of property)
TotalLivingArea - Numeric (Living Area of property)
Bedrooms - Numeric        (total bedrooms in house)
FinishedBsmtArea - Numeric  (FInsihed basement work)
LotArea - Numeric  (Area of total parking lot)
AC - character (If ac is present or not)
FirePlace - character   (Fireplace present or not)
Neighborhoor - Factor   (neighborhood located in)

We expect their data range to be generally between their highest and lowest values. For AC,Fireplace we can have NA or Present. 
 

<<<<<<< HEAD
=======
=======
>>>>>>> 4aec923a397186abcfb3323cfbff9642c7a0d504

2. is there a variable of special focus?
 - the variables we want to look at are Sale Price and TotalLivingArea (sf)
 
Both are numeric variables
<<<<<<< HEAD

Sale price is the main variable and total living area is the variable that might be related
 
 #Step Three
=======
#Step Three
>>>>>>> 35ed1ec6b32361c60c078eddc0666aede76999c1
=======
>>>>>>> 4aec923a397186abcfb3323cfbff9642c7a0d504


 
 P
>>>>>>> c925fe450723b846485fb6ad26fb09d56e3b7678
 
```{r}
library(ggplot2)
range(ames$`Sale Price`)



ggplot(ames, aes(x = log(`Sale Price`))) +
  geom_histogram(binwidth = 0.1, fill = "skyblue", color = "black") +
  labs(x = "Log(Sale Price)", y = "Frequency", title = "Distribution of Log(Sale Price)") +
  theme_minimal()
  

```
<<<<<<< HEAD


library(ggplot2)

```{r}
ggplot(ames, aes(x = 'TotalLivingArea (sf)', y = 'Sale Price')) +
  geom_point() +
  labs(x = "TotalLivingArea (sf)", y = "Sale Price", title = "Scatterplot of Sale Price vs. Total Living Area")


```

#Step Four
```{r}
cleaned_data <- na.omit(ames$`TotalLivingArea (sf)`)

range_var <- range(cleaned_data)
print(range_var)

```

```{r}
ggplot(aes(x = 'Sale Price', y = `TotalLivingArea (sf)` ), data=ames) +
  geom_boxplot() +
  coord_flip()
  
```
General pattern is bell shaped curve with concentrated frequency around 12.5. Oddities is outliers around sale price 0 and 20.
